%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{С++ \& Gamedev Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\begin{cventries}

  \cventry
    {Game Development}
    {Personal Projects}
    {2023 -- Present}
    {}
    {
      {\small{\textit{}}}
      \vspace{0.0em}
      \begin{cvitems}
        \item {Worked with Unreal Engine 5 in C++, completing an Unreal Engine C++ course and implementing a simple first-person shooter prototype.}
        \item {Implemented basic gameplay AI experiments in Unreal Engine, including exploration of GOAP-style decision logic in small prototypes.}
        \item {Built small interactive gameplay prototypes in Unity (mobile-style mechanics such as Tetris and draw-to-move) and in C++ using SFML (2D arcade-style airplane control game).}
      \end{cvitems}
    }

  \cventry
    {Research Engineer \& Principal C++ Developer} % Job title
    {ABBYY (CoreOCR Team)} % Organization
    {Nov. 2021 - Oct. 2024} % Date(s)
    {Novi Sad, Serbia, Hybrid} % Location
    {
      {\small{\textit{Global technology company specializing in document processing and OCR.}}}
      \vspace{1.2em}
      \begin{cvitems}
        \item {Implemented performance-critical C++ machine learning components for text layout analysis, improving recognition quality on noisy and complex documents.}
        \item {Reduced memory usage and improved runtime efficiency of production inference pipelines.}
        \item {Improved robustness of post-recognition language processing by tuning classical language models and heuristic logic.}
        \item {Debugged and fixed a critical SIMD-related crash by analyzing cross-platform crash dumps and investigating AVX-specific C++ code paths.}
      \end{cvitems}
    }

  \cventry
    {Computer Vision Researcher \& C++ Developer} % Job title
    {Intelligent Security Systems} % Organization
    {Oct. 2016 - Nov. 2018} % Date(s)
    {Moscow, Russia, On-site} % Location
    {
      {\small{\textit{Engineering company focused on computer vision–based security solutions.}}}
      \vspace{1.2em}
      \begin{cvitems}
        \item {Developed and improved license plate recognition (LPR) algorithms in C++ using classical computer vision techniques.}
        \item {Optimized real-time image processing pipelines with multithreading and SIMD (SSE) to meet performance constraints.}
        \item {Extended recognition systems to related domains such as cargo and railway carriage number recognition.}
      \end{cvitems}
    }
\end{cventries}

\needspace{6\baselineskip}
\cvsection{Python \& Computer Vision \& ML Experience}
\begin{cventries}
  \cventry
    {Lead Computer Vision Engineer \& Consultant}
    {Rescope}
    {Jun. 2025 -- Jan. 2026}
    {San Francisco, US, Remote}
    {
      {\small{\textit{Early-stage startup focused on AI-driven analysis of buildings and architectural data.}}}
      \vspace{1.2em}
      \begin{cvitems}
        \item {Led and delivered multiple computer vision projects in the domain of building and floorplan analysis, covering satellite imagery, architectural PDFs, and vector and raster floorplans.}
        \item {Designed and implemented end-to-end pipelines for extracting structured building data from heterogeneous sources under evolving product requirements and technical uncertainty.}
        \item {Owned data strategy and preparation, including dataset collection and annotation workflows, and advised founders on product scope, feasibility, and engineering effort.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Head of Computer Vision \& Senior Computer Vision Engineer} % Job title
    {DataNerdsAI} % Organization
    {Nov. 2018 - Nov. 2021} % Date(s)
    {Moscow, Russia, On-site} % Location
    {
      {\small{\textit{Computer vision consultancy delivering applied AI solutions for industrial domains.}}}
      \vspace{1.2em}
      \begin{cvitems}
        \item {Led the computer vision direction, combining hands-on engineering with technical leadership, system design, and direct customer interaction.}
        \item {Delivered multiple production-ready computer vision systems for agriculture and logistics, working end-to-end from problem definition to on-site deployment under real-world constraints.}
      \end{cvitems}
    }

%---------------------------------------------------------


    \cventry
    {Owner / Operator} % Job title
    {Small Local Business in Serbia} % Organization
    {Nov. 2024 - Jun. 2025} % Date(s)
    {Novi Sad, Serbia, On-site} % Location
    {
      {\small{\textit{}}}
      \vspace{0.0em}
      \begin{cvitems}
        \item {Direct responsibility for running and operating a small business, including hiring, payroll, taxes, cost control, and day-to-day operations.}
        \item {Hands-on experience making decisions under financial, legal, and operational constraints, with full accountability for outcomes.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
